An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-28 VLDB2026/main.tex
change 4.2.2 and 3.3

	\noindent\textbf{\underline{VBASE \cite{vbase}.}}  
	Similar to PASE, VBASE is a PostgreSQL-based vector indexing plugin supporting HNSW, SPTAG~\cite{sptag}, and SPANN~\cite{spann}. We focus on HNSW-based search. VBASE adopts a post-filtering strategy. However, it employs an iterative filtering mechanism: during index traversal, each node is immediately checked against the WHERE clause, and non-matching nodes are discarded. This avoids the issue in PASE where the final result set may contain fewer than $k$ results.

@@

	\textit{\textbf{Multi-Attribute Building and Single-Attribute Query.}}
	In this scenario, the index is constructed using 8 attributes but applies filtering condition on only 1 attribute during the query process.
	\textcolor{blue}{The original NHQ implementation does not support this scenario. We modified the code to enable this experiment.}

>>>>

	\noindent\textbf{\underline{VBASE \cite{vbase}.}}  
	Similar to PASE, VBASE is a PostgreSQL-based vector indexing plugin supporting HNSW, SPTAG~\cite{sptag}, and SPANN~\cite{spann}. \textcolor{red}{We focus on HNSW-based search because SPTAG and SPANN have poorer performance and their source code does not fully implement index-building functionality}. VBASE adopts a post-filtering strategy. However, it employs an iterative filtering mechanism: during index traversal, each node is immediately checked against the WHERE clause, and non-matching nodes are discarded. This avoids the issue in PASE where the final result set may contain fewer than $k$ results.

@@

	\textit{\textbf{Multi-Attribute Building and Single-Attribute Query.}}
	In this scenario, the index is constructed using 8 attributes but applies filtering condition on only 1 attribute during the query process.
	\textcolor{red}{We modified the NHQ source code to support this experiment.}
